Numerical simulation of bubble deformation \\ and breakup under simple linear shear flows

### 2024-11-17 Revised-paper/Paper/Bubble-deformation-Rev.tex
grammar fixes

\begin{abstract}
\textcolor{red}
{
Numerical simulations are presented for the deformation and breakup of a bubble in liquids undergoing simple linear shear flow.  Numerical results are obtained using a projection method for incompressible two-phase flow in which the method represents interfaces using the sharp interface coupled level set and volume of fluid (CLSVOF) method.   To verify our numerical algorithm and provide a basis for comparison, we also present simulation results that compare with previous, more popular, drop deformation and rupture simulations.  The numerical results reveal that the shear-induced bubble deformation and breakup process differs significantly from that of the analogous drop system under similar flow conditions.  The first distinguishing factor for bubble breakup is that the magnitude of shear flow necessary for causing rupture is much larger than that in the drop system case.  In other words, a larger Reynolds number is needed to induce bubble breakup.  The second distinct feature of the bubble system versus the drop system is that the bubble does not maintain a stable deformed shape as the system parameters approach the critical ``breakup'' Reynolds number.  It is asserted that the differences in morphology for a bubble undergoing breakup versus a drop in the same process can be attributed to the density and viscosity ratio of the corresponding two-phase flow systems.  The critical conditions for bubble breakup with respect to the Reynolds and capillary numbers are determined for several cases.  }
\end{abstract}

@@

Bubble dynamics in shear flow, including breakup, is critically important for various \textcolor{blue} {gas-liquid} scientific and engineering processes. 
We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, 
microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble}. 
In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  
Studying bubble break-up, vis a vis that of the drop, via computation rather than (terrestrial) experiments simplifies the process of setting a combination of precise, simple shear 
flow conditions, low $Ca$ ($Ca=\mu_{m}U/\sigma$) conditions, low-density ratio, and low viscosity ratios.  The physical properties that distinguish 
bubble and drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} / \rho_{\rm m}$ and the viscosity 
ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' 
denote the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble, viscous liquid, $\lambda \simeq 0$ 
and $\eta \simeq 0$, whereas most (terrestrial) studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.  
In this work, we focus on identifying critical flow states numerically, in terms of dimensionless quantities, that specify the extreme 
conditions at which a bubble in shear flow first transitions from deformation to breakup.  We validate our numerical method by examining 
the sensitivity of the critical bubble deformation and break-up flow states with respect to the grid size.  An advantage of studying shear-driven 
bubble deformation and breakup computationally rather than experimentally is that we can easily modify fluid physical properties and external properties (e.g. the gravity force, in order to compare with the analogous drop case) in order to isolate
the sensitivity of deformation and breakup to physical parameters.  In our computations, the time-evolution of the boundary 
between gas and liquid is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface capturing algorithm \cite{SusPuc00,SusSmiHusOhtZhi07}.  The rationale for the CLSVOF method is that the hybrid method represents the (complex) gas-liquid interfaces with minimal volume loss (property of the volume-of-fluid method) and minimal error in the approximation of the surface tension force (property of the level set method).
We focus on determining critical physical conditions in which the breakup of a bubble occurs in shear flow because it is important to identify 
the parameter regimes in which a relatively simple system transitions from stable to unstable.  Specifically, we ascertain the critical 
Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as a function of $Ca$.          
In previous studies on the motion of bubble deformation in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings 
for bubble deformation under very low $Re$ number conditions ($Re \ll 1$) have been reported.  This is understandable since a low Reynolds number matrix fluid mitigates the effect of gravity on distorting the comparison with the drop case.  In this work, we determine, for the 
first time, the critical Reynolds number ($Re \gg 1$) that leads to bubble breakup.  Additionally, our computational studies 
reveal characteristics that distinguish a drop's deformation and breakup processes versus those of a bubble.
We remark that there have been a number of articles on the study of lift of slightly deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.  
We reiterate, though, that for bubble deformation and breakup in shear flows, only a few articles exist: \cite{WeiQiaXu12,WanShiZha15,AAMM-16-2}.
These previous studies mainly examined the dynamics (e.g., rotation angle) of bubble deformation in shear flow.
Concerning bubble breakup, Wei et al.~\cite{WeiQiaXu12} presented one numerical result for a bubble breakup process under the condition of $Ca$ (capillary number) = 35. Sharifi et al\cite{AAMM-16-2} presented two results for bubble breakup corresponding to $Ca=7.5$ and $Ca=11.2$.  We point out that all of the previous
computational research on bubble deformation (and breakup) under shear driven 
flow\cite{WeiQiaXu12,WanShiZha15,AAMM-16-2}  use the (explicit) Lattice Boltzmann method.  For accurately computing the tensile strength of a bubble, and accurately computing threshold parameters for break-up (what we do in this article, and what was not done in previous work), it is critical that a numerical method directly enforces the velocity continuity condition and the gas-liquid interface normal jump conditions.  We contend that a projection method (e.g. this paper and \cite{zhang2021three,zhang2022three,OhtSus12}) is the more appropriate (albeit slower) method for our study rather than the Lattice Boltzmann method.  Also, in contrast to the Lattice Boltzmann method, our interface ``capturing'' method, the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07},  maintains the gas/liquid interface as sharp, enables accurate approximation of the surface tension force,  and by construction the CLSVOF method preserves mass and volume within a fraction of a percent. The results that we present in this article (see e.g. section \ref{convergence}) regarding measuring the tensile strength of a bubble are unique and validated with respect to comparisons with previous experimental data and grid refinement studies.  Admittadly, each simulation on the finest resolution takes over a half a year to complete on a workstation because of the following unavoidable factors: (i) the large density-ratio projection method requires the solution of a large sparse, ill-conditioned, matrix system at each time step, (ii) the finer the mesh, the more precise the measured threshold, and right at the threshold (Taylor Deformation parameter $D\approx 1$!), oscillatory behaviour is observed delaying the determination of breakup or not.  Finally, the larger the deformation parameter $D$, the longer we must make our computational domain (bigger domain aspect ratio!) thereby adversely effecting the condition number even more for carrying our the pressure projection. \\ \indent
To highlight the mechanisms of bubble deformation and breakup in a shear flow, we juxtapose the bubble results with those of a drop (for terrestrial experiments, when the density ratio of drop to matrix is very close to one!).
We remark that while the study of critical tensile strength parameters for the bubble is sparse, there have been many studies for the 
simpler drop problem. For completeness, we give a brief overview of previous ``tensile strength'' studies pertaining to drops.
The study of the deformation and breakup of a drop in immiscible viscous liquids undergoing simple linear shear flow has been investigated 
extensively due to its fundamental importance to emulsion processes, materials processing, mixing, and reaction devices.The pioneering 
experimental work on this problem was performed by Taylor in the early 1930s \cite{Tay32, Tay34}, and the subsequent theoretical and 
experimental progress up to the 1980s and 1990s was reviewed in \cite{Ral84} and \cite{Sto94}, respectively.  By the 2000s, progress in 
computational fluid dynamics (CFD) techniques and increased access to powerful computing resources led to a surge of research focused 
on direct simulations of this problem.  In particular, detailed computational investigations of drop breakup, based on a Volume-of-Fluid (VOF) 
method \cite{HirNic81} were presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2, RenCriLi02,KhiRenCri03,Ren06,Ren07,Ren08-2}. 
Since then, the literature on computational studies on the deformation and breakup of a single or several drops in shear flow has continued 
to grow \cite{CriGuiAlfBlaLoe03, InaTomOgi03,ZhaMikBan06, BazAndMei06, JanAnd08, CroGriSch10,KomShaEskDer14,KomShaEskDer15, 
IoaLiuZha16, HerRan17,AmaBalCasOli19, ZhaShuGuaYan21} and a variety of numerical techniques have been developed to tackle this 
problem, including boundary-integral approaches \cite{CriBlaLoe01, JanAnd07}, lattice Boltzmann methods \cite{Ina06, KomShaEskDer14}, 
front tracking schemes \cite{UnvTry92}, and interface-capturing level set methods \cite{SusSmeOsh94}.

@@

Thus, a lot of studies about the deformation and breakup of a drop in simple linear shear have been presented so far. In contrast, few
 studies have been conducted on bubble deformation and breakup.  We reiterate why there have been few studies regarding the ``tensile strength'' of bubbles. Experimentally, in the moderate to high Reynolds number regime, and low Capillary number regime, one is restricted to microgravity conditions.  Computational experiments are difficult too. In order to accurately compute the tensile strength of a bubble, one must resort to a combination of 
parallel computing, the multigrid preconditioned conjugate gradient method\cite{tatebe1993multigrid,SusSmiHusOhtZhi07} for poorly conditioned large sparse matrix systems, adaptive mesh refinement\cite{AMReX_JOSS,SusSmiHusOhtZhi07}, and a robust, volume preserving interface tracking method (we use the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07}).

@@

Figure~\ref{fig:SchemAndGrid}(a) shows a schematic of the computational system
for our studies of a bubble (or drop) in shear flow.  The computational domain
consists of a three-dimensional rectangular domain of $L$ (length) $\times$ $W$
(width) $\times$ $H$ (height).  The size of $L$, $W$ and $H$ was determined
after consideration of numerical result sensitivity to domain size; numerical
studies of domain-size dependence are presented in
Section~\ref{sec:DomGrdSize}.  All computational results that follow were
obtained from numerical solutions of the three-dimensional governing equations
for gas-liquid/liquid-liquid flows.  Computations are initialized with a
spherical bubble (or drop) of radius $R$ = 5 mm set at the center of the
computational domain.   The bubble (or drop) is then subjected to a linear
shear flow generated by the motion of the top and bottom plates, which have
constant velocity $+V$ and $-V$, respectively.  In the interior of the domain,
the initial velocity condition is assumed to be a simple linear profile and
periodic boundary conditions are imposed along the $x$ and $y$ directions.
Mathematically, the initial and boundary conditions are described as follows:
%
\begin{eqnarray}
	\phi(x,y,z,0)=\sqrt{(x-\frac{L}{2})^{2}+(y-\frac{W}{2})^{2}+
	(z-\frac{H}{2})^{2}}-R \label{IC_BC} \\
	\bmu(x,y,z,0)=\left( \begin{array}{c}
		\frac{2V}{H}(z-\frac{H}{2}) \\ 0 \\ 0 
	\end{array} \right) \nonumber \\
	\phi(x+L,y,z,t)=\phi(x,y,z,t) \hspace{20pt}
	\phi(x,y+W,z,t)=\phi(x,y,z,t) \nonumber \\
	\bmu(x,y,H,t)=\left( \begin{array}{c}
		                V \\ 0 \\ 0 
	\end{array} \right)  \hspace{20pt}
	\bmu(x,y,0,t)=\left( \begin{array}{c}
		                -V \\ 0 \\ 0 
	\end{array} \right)  \nonumber \\
	\bmu(x+L,y,z,t)=\bmu(x,y,z,t) \hspace{20pt} 
	\bmu(x,y+W,z,t)=\bmu(x,y,z,t) \nonumber
\end{eqnarray}
%
$\phi(x,y,z,t)$ is a material indicator function which is positive in the
``matrix'' fluid and negative in the bubble (or drop) fluid.  $\bmu(x,y,z,t)$
is the velocity.

Common dimensionless physical parameters used to describe gas-liquid or
liquid-liquid two-phase flows include the Reynolds ($Re$), Weber ($We$) (or
$Ca$ (= $We/Re$)) and Froude ($Fr$) numbers.  Gas-Liquid and Liquid-Liquid
two-phase flow problems are also determined by the density ratio $\lambda$ and
the viscosity ratio $\eta$.  In the present study, in order to clearly isolate only the effects 
of $\lambda$ and $\eta$, the effect of gravity is not considered ($g = 0$) so that 
we ignore the effect of the $Fr$ number 
\textcolor{red}
{
$\left(= \frac{{\it \Gamma}R}{\sqrt {gR}} \right)$.
}

When comparing with previous drop studies, we fix $\lambda=1$ for the drop cases.  As a result,
(for $\lambda=1$) the following dimensionless physical parameters are used to
describe the problem of drop deformation/breakup in shear flow
%
\begin{eqnarray}\label{dimensonless}
  Re = \frac{\rho_{\rm m}UR}{\mu_{\rm m}}, \quad
  Ca = \frac{\mu_{\rm m}U}{\sigma}, \quad
  \eta = \frac{\mu_{\rm b}}{\mu_{\rm m}} 
	\hspace{20pt} m=\mbox{matrix fluid}
\end{eqnarray}
%
$U$ is the velocity scale and $\sigma$ denotes the surface tension.  For the
problem of shear-induced drop deformation and breakup, the velocity is set to
$U = \mathit{\Gamma} R$, where the shear-rate is $\mathit{\Gamma} = 2V/H$.  As
mentioned in the introduction, most previous drop studies set $\eta = 1$ (e.g.
\citet{LiRenRen00}).  Thus, for comparison with previous drop deformation and
breakup problems, we set $\lambda = \eta = 1$ (and also neglect the effect of
gravity so that $g=0$). On the other hand, in our computations for bubble
deformation, we set the density and viscosity of air to be $\rho_{\rm b}$ = 1.2
kg/m$^{3}$ and $\mu_{\rm b} = 1.8 \times 10^{-5}$ Pa$\cdot$s respectively.  We
emphasize that for consistency with previous studies (\citet{LiRenRen00,
RusMan02, MulTobDreFisWin08, KomShaEskDer14, AmaBalCasOli19}), we
computationally examine the deformation and breakup of a bubble in simple
linear shear flow as a function of the $Re$ and $Ca$ numbers.  That is to say,
by setting $g=0$, we are isolating the effect of only varying $Re$ and $Ca$ on
bubble deformation and breakup.  In our controlled study, we determine the
critical $Re_{\rm c}$ versus $Ca$ curve in which $Re_{\rm c}$ corresponds to
the threshold of bubble (or drop) breakup.  We determine the critical $Re_{\rm
c}$ versus $Ca$ curve for strategic pairs of the density ratio and viscosity
ratio.

In our computations, the density of the matrix fluid is fixed at $\rho_{\rm m}$
= 1000 kg/m$^3$.  The surface tension at the bubble (drop) interface is $\sigma
=2.5 \times 10^{-2}$ N/m. The values of $Re$ and $Ca$ in our simulations are
controlled by changing the values of $\mu_{\rm m}$ and $V$. 
\textcolor{red}
{
Specifically, we set $\mu_{\rm m} = 2.0 \times 10^{-2} \sim 6.0 \times 10^{-2}$ Pa$\cdot$s and
$V$ = about 1.1 $\sim$ 1.3 m/s.
As a consequence, 
}
for studying bubble deformation and break-up, the density and viscosity ratios satisfy
$\lambda = 1.2 \times 10^{-3}$ and $\eta < 1.0 \times 10^{-3}$.

\textcolor{red}
{
For readers’ reference, we describe the effect of gravity here. When we apply $g$ = 9.8 m/$s^{2}$,  $Fr$  can be $Fr$ = $1.7 \sim 1.9$ in our computations.
Although the values of $Fr$ are not so large, the effect of gravity (bubble rise motion) may not be completely negligible in terms of $Fr$.
However, bubbles in our computations reach the breakup by way of deformation very quickly at $t$ = about 0.5 s. 
Accordingly, it is expected that the effect of gravity (bubble rise motion) can be small for the behavior of bubble deformation and breakup 
around critical $Re$ number conditions in our study.
}
%  -----------------------------------------------------------------------------
\section{Numerical Analysis}
%  -----------------------------------------------------------------------------
% 
%\begin{comment} 
\begin{figure}%[h!]
%  \includegraphics[width=\textwidth]{1-SchematicAndGrid}
  \centering
  \includegraphics[scale=0.4]{Figure/1-SchematicAndGrid}
  \caption{(a) Computational domain schematic for a bubble or drop in shear 
           flow.  Gravity is set to zero in our computations in order to isolate
           the effects of density and viscosity ratios.  
           (b) (\textit{upper panel}) a two-level adaptive mesh 
           refinement (AMR) grid schematic corresponding to one of our
           simulations;
           (\textit{lower panel}) snapshot of bubble deformation 
           in simple linear shear flow.}
  \label{fig:SchemAndGrid}
\end{figure}
%\end{comment}
%

>>>>

\begin{abstract}
\textcolor{red}
{
Numerical simulations are presented for the deformation and breakup of a bubble in liquids undergoing simple linear shear flow.  Numerical results are obtained using a projection method for incompressible two-phase flow. The method represents interfaces using the sharp interface coupled level set and Volume-Of-Fluid (CLSVOF) method.   To verify our numerical algorithm and provide a basis for comparison, we also present simulation results that compare with previous, more popular, drop deformation and rupture simulations.  The numerical results reveal that the shear-induced bubble deformation and breakup process differs significantly from that of the analogous drop system under similar flow conditions.  The first distinguishing factor for bubble breakup is that the magnitude of shear flow necessary for causing rupture is much larger than that in the drop system case.  In other words, a larger Reynolds number is needed to induce bubble breakup.  The second distinct feature of the bubble system versus the drop system is that the bubble does not maintain a stable deformed shape as the system parameters approach the critical ``breakup'' Reynolds number.  It is asserted that the differences in morphology for a bubble undergoing breakup versus a drop in the same process can be attributed to the density and viscosity ratio of the corresponding two-phase flow systems.  The critical conditions for bubble breakup with respect to the Reynolds and capillary numbers are determined for several cases. }
\end{abstract}

@@

\textcolor{red} {
Bubble dynamics in shear flow, including breakup, is critically important for various \textcolor{blue} {gas-liquid} scientific and engineering processes.  We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble}.  In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
\par
\textcolor{red} {
This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  Studying bubble break-up, in which we focus only on the balance of the wall driving force and bubble surface tension force, via computation rather than (terrestrial) experiments simplifies the process of setting a combination of precise, simple shear flow conditions, low $Ca$ ($Ca=\mu_{m}U/\sigma$) conditions, low-density ratio, and low viscosity ratios.  The physical properties that distinguish bubble and drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} / \rho_{\rm m}$ and the viscosity ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' denote the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble, viscous liquid, $\lambda \simeq 0$ and $\eta \simeq 0$, whereas most (terrestrial) studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.  
\par
\textcolor{red} {
In this work, we focus on identifying critical flow states numerically, in terms of dimensionless quantities, that specify the extreme conditions at which a bubble in shear flow first transitions from deformation to breakup.  We validate our numerical method by examining the sensitivity of the critical bubble deformation and break-up flow states with respect to the grid size.  An advantage of studying shear-driven bubble deformation and breakup computationally rather than experimentally is that we can easily modify fluid physical properties and external properties (e.g. we can easily modify the gravity force, in order to compare with the analogous drop case or compare with microgravity conditions) in order to isolate the sensitivity of deformation and breakup to physical parameters.  In our computations, the time-evolution of the boundary between gas and liquid is tracked with a Coupled-Level-Set and Volume-Of-Fluid (CLSVOF) interface capturing algorithm \cite{SusPuc00,SusSmiHusOhtZhi07}.  The rationale for the CLSVOF method is that the hybrid method represents the (complex) gas-liquid interfaces with minimal volume loss (property of the Volume-Of-Fluid method) and minimal error in the approximation of the surface tension force (property of the Level-Set method).
\par
\textcolor{red} {
We focus on determining critical physical conditions in which the breakup of a bubble occurs in shear flow because it is important to identify the parameter regimes in which a relatively simple system transitions from stable to unstable.  Specifically, we ascertain the critical Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as a function of $Ca$.  
\par
In previous studies on the motion of bubble deformation in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low $Re$ number conditions ($Re \ll 1$) have been reported.  This is understandable since a low Reynolds number matrix fluid mitigates the effect of gravity on distorting the comparison with the drop case.  In this work, we determine, for the first time, the critical Reynolds number ($Re \gg 1$) that leads to bubble breakup.  Additionally, our computational studies reveal characteristics that distinguish a drop's deformation and breakup processes versus those of a bubble.
\par
\textcolor{red} {
We remark that there have been a number of articles on the study of lift of slightly deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.  We reiterate, though, that for bubble deformation and breakup in shear flows, only a few articles exist: \cite{WeiQiaXu12,WanShiZha15,AAMM-16-2}.  These previous studies mainly examined the dynamics (e.g., rotation angle) of bubble deformation in shear flow.  Concerning bubble breakup, Wei et al.~\cite{WeiQiaXu12} presented one numerical result for a bubble breakup process under the condition of $Ca$ (capillary number) = 35. Sharifi et al\cite{AAMM-16-2} presented two results for bubble breakup corresponding to $Ca=7.5$ and $Ca=11.2$.  We point out that all of the previous computational research on bubble deformation (and breakup) under shear driven flow\cite{WeiQiaXu12,WanShiZha15,AAMM-16-2} use the (explicit) Lattice Boltzmann method.  For accurately computing the tensile strength of a bubble, and accurately computing threshold parameters for break-up (what we do in this article, and what was not done in previous work), it is critical that a numerical method directly enforces the velocity continuity condition and the gas-liquid interface normal jump conditions.  We contend that a projection method (e.g. this paper and \cite{zhang2021three,zhang2022three,OhtSus12}) is the more appropriate (albeit slower) method for our study rather than the Lattice Boltzmann method.  Also, in contrast to the Lattice Boltzmann method, our interface ``capturing'' method, the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07}, maintains the gas/liquid interface as sharp, enables accurate approximation of the surface tension force,  and by construction the CLSVOF method preserves mass and volume within a fraction of a percent. The results that we present in this article (see e.g. section \ref{convergence}) regarding measuring the tensile strength of a bubble are unique and validated with respect to comparisons with previous experimental data and grid refinement studies.  Admittadly, each simulation on the finest resolution takes over a half a year to complete on a workstation because of the following unavoidable factors: (i) the large density-ratio projection method requires the solution of a large sparse, ill-conditioned, matrix system at each time step, (ii) the finer the mesh, the more precise the measured threshold, and right at the threshold (Taylor Deformation parameter $D\approx 1$!), oscillatory behaviour is observed delaying the determination of breakup or not.  Finally, the larger the deformation parameter $D$, the longer we must make our computational domain (bigger domain aspect ratio!) thereby adversely effecting the condition number even more for carrying our the pressure projection. 
\par
\textcolor{red} {
To highlight the mechanisms of bubble deformation and breakup in a shear flow, we juxtapose the bubble results with those of a drop (for terrestrial experiments, when the density ratio of drop to matrix is very close to one!).  We remark that while the study of critical tensile strength parameters for the bubble is sparse, there have been many studies for the simpler drop problem. For completeness, we give a brief overview of previous ``tensile strength'' studies pertaining to drops.
\par
\textcolor{red} {
The study of the deformation and breakup of a drop in immiscible viscous liquids undergoing simple linear shear flow has been investigated extensively due to its fundamental importance to emulsion processes, materials processing, mixing, and reaction devices.  The pioneering experimental work on this problem was performed by Taylor in the early 1930s \cite{Tay32, Tay34}, and the subsequent theoretical and experimental progress up to the 1980s and 1990s was reviewed in \cite{Ral84} and \cite{Sto94}, respectively.  By the 2000s, progress in computational fluid dynamics (CFD) techniques and increased access to powerful computing resources led to a surge of research focused on direct simulations of this problem.  In particular, detailed computational investigations of drop breakup, based on a Volume-of-Fluid (VOF) method \cite{HirNic81} were presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2, RenCriLi02,KhiRenCri03,Ren06,Ren07,Ren08-2}.  Since then, the literature on computational studies on the deformation and breakup of a single or several drops in shear flow has continued to grow \cite{CriGuiAlfBlaLoe03, InaTomOgi03,ZhaMikBan06, BazAndMei06, JanAnd08, CroGriSch10,KomShaEskDer14,KomShaEskDer15, IoaLiuZha16, HerRan17,AmaBalCasOli19, ZhaShuGuaYan21} and a variety of numerical techniques have been developed to tackle this problem, including boundary-integral approaches \cite{CriBlaLoe01, JanAnd07}, lattice Boltzmann methods \cite{Ina06, KomShaEskDer14}, front tracking schemes \cite{UnvTry92}, and interface-capturing level set methods \cite{SusSmeOsh94}.
\par

@@

{ Thus, a lot of studies about the deformation and breakup of a drop in simple linear shear have been presented so far. In contrast, few studies have been conducted on bubble deformation and breakup.  We reiterate why there have been few studies regarding the ``tensile strength'' of bubbles. Experimentally, if one wants to isolate the interplay of shearing force with the bubble surface tension force, in the moderate to high Reynolds number regime, and low Capillary number regime, one is restricted to microgravity conditions.  Computational experiments are difficult too. In order to accurately compute the tensile strength of a bubble, one must resort to a combination of parallel computing, the multigrid preconditioned conjugate gradient method\cite{tatebe1993multigrid,SusSmiHusOhtZhi07} for poorly conditioned large sparse matrix systems, adaptive mesh refinement\cite{AMReX_JOSS,SusSmiHusOhtZhi07}, and a robust, volume preserving interface tracking method (we use the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07}).

@@

Figure~\ref{fig:SchemAndGrid}(a) shows a schematic of the computational system for our studies of a bubble (or drop) in shear flow.  The computational domain consists of a three-dimensional rectangular domain with the dimensions of $L$ (length) $\times$ $W$ (width) $\times$ $H$ (height).  The size of $L$, $W$ and $H$ was determined after consideration of the sensitivity of numerical results to the domain size; numerical studies of domain-size dependence are presented in Section~\ref{sec:DomGrdSize}.  All computational results that follow were obtained from numerical solutions of the three-dimensional governing equations for gas-liquid/liquid-liquid flows.  Computations are initialized with a spherical bubble (or drop) of radius $R$ = 5 mm set at the center of the computational domain.   The bubble (or drop) is then subjected to a linear shear flow generated by the motion of the top and bottom plates, which have constant velocity $+V$ and $-V$, respectively.  In the interior of the domain, the initial velocity condition is assumed to be a simple linear profile and periodic boundary conditions are imposed along the $x$ and $y$ directions.  Mathematically, the initial and boundary conditions are described as follows: 
%
\begin{eqnarray}
	\phi(x,y,z,0)=\sqrt{(x-\frac{L}{2})^{2}+(y-\frac{W}{2})^{2}+
	(z-\frac{H}{2})^{2}}-R \label{IC_BC} \\
	\bmu(x,y,z,0)=\left( \begin{array}{c}
		\frac{2V}{H}(z-\frac{H}{2}) \\ 0 \\ 0 
	\end{array} \right) \nonumber \\
	\phi(x+L,y,z,t)=\phi(x,y,z,t) \hspace{20pt}
	\phi(x,y+W,z,t)=\phi(x,y,z,t) \nonumber \\
	\bmu(x,y,H,t)=\left( \begin{array}{c}
		                V \\ 0 \\ 0 
	\end{array} \right)  \hspace{20pt}
	\bmu(x,y,0,t)=\left( \begin{array}{c}
		                -V \\ 0 \\ 0 
	\end{array} \right)  \nonumber \\
	\bmu(x+L,y,z,t)=\bmu(x,y,z,t) \hspace{20pt} 
	\bmu(x,y+W,z,t)=\bmu(x,y,z,t) \nonumber
\end{eqnarray}
%
$\phi(x,y,z,t)$ is a material indicator function which is positive in the
``matrix'' fluid and negative in the bubble (or drop) fluid.  $\bmu(x,y,z,t)$
is the velocity.

Common dimensionless physical parameters used to describe gas-liquid or
liquid-liquid two-phase flows include the Reynolds ($Re$), Weber ($We$) (or
$Ca$ (= $We/Re$)) and Froude ($Fr$) numbers.  Gas-Liquid and Liquid-Liquid
two-phase flow problems are also determined by the density ratio $\lambda$ and
the viscosity ratio $\eta$.  In the present study, in order to clearly isolate the effects of $\lambda$ and $\eta$, and isolate the balance of the driving wall force with the bubble surface tension force, the effect of gravity is not considered ($g = 0$) so that we ignore the effect of the $Fr$ number 
\textcolor{red}
{
$\left(= \frac{{\it \Gamma}R}{\sqrt {gR}} \right)$.
}

When comparing with previous drop studies, we fix $\lambda=1$ for the drop cases.  As a result, (for $\lambda=1$) the following dimensionless physical parameters are used to describe the problem of drop deformation/breakup in shear flow:
\begin{eqnarray}\label{dimensonless}
  Re = \frac{\rho_{\rm m}UR}{\mu_{\rm m}}, \quad
  Ca = \frac{\mu_{\rm m}U}{\sigma}, \quad
  \eta = \frac{\mu_{\rm b}}{\mu_{\rm m}} 
	\hspace{20pt} m=\mbox{matrix fluid}
\end{eqnarray}
$U$ is the velocity scale and $\sigma$ denotes the surface tension.  For the problem of shear-induced drop deformation and breakup, the velocity is set to $U = \mathit{\Gamma} R$, where the shear-rate is $\mathit{\Gamma} = 2V/H$.  As mentioned in the introduction, most previous drop studies set $\eta = 1$ (e.g.  \citet{LiRenRen00}).  Thus, for comparison with previous drop deformation and breakup problems, we set $\lambda = \eta = 1$ (and also neglect the effect of gravity so that $g=0$). On the other hand, in our computations for bubble deformation, we set the density and viscosity of air to be $\rho_{\rm b}$ = 1.2 kg/m$^{3}$ and $\mu_{\rm b} = 1.8 \times 10^{-5}$ Pa$\cdot$s respectively.  We emphasize that for consistency with previous studies (\citet{LiRenRen00, RusMan02, MulTobDreFisWin08, KomShaEskDer14, AmaBalCasOli19}), we computationally examine the deformation and breakup of a bubble in simple linear shear flow as a function of the $Re$ and $Ca$ numbers.  That is to say, by setting $g=0$, we are isolating the effect of only varying $Re$ and $Ca$ on bubble deformation and breakup.  In our controlled study, we determine the critical $Re_{\rm c}$ versus $Ca$ curve in which $Re_{\rm c}$ corresponds to the threshold of bubble (or drop) breakup.  We determine the critical $Re_{\rm c}$ versus $Ca$ curve for strategic pairs of the density ratio and viscosity ratio.
\par
In our computations, the density of the matrix fluid is fixed at $\rho_{\rm m}$ = 1000 kg/m$^3$.  The surface tension at the bubble (drop) interface is $\sigma =2.5 \times 10^{-2}$ N/m. The values of $Re$ and $Ca$ in our simulations are controlled by changing the values of $\mu_{\rm m}$ and $V$.  
Specifically, we set $\mu_{\rm m} = 2.0 \times 10^{-2} \sim 6.0 \times 10^{-2}$ Pa$\cdot$s and
$V$ = about 1.1 $\sim$ 1.3 m/s.
As a consequence, 
for studying bubble deformation and break-up, the density and viscosity ratios satisfy
$\lambda = 1.2 \times 10^{-3}$ and $\eta < 1.0 \times 10^{-3}$.
\par
For readers’ reference, we describe the effect of gravity here. When we apply $g$ = 9.8 m/$s^{2}$,  $Fr$  can be $Fr$ = $1.7 \sim 1.9$ in our computations.  Although the values of $Fr$ are not so large, the effect of gravity (bubble rise motion) may not be completely negligible in terms of $Fr$.  However, bubbles in our computations reach the breakup by way of deformation very quickly at $t$ = about 0.5 s.  Accordingly, it is expected that the effect of gravity (bubble rise motion) can be small for the behavior of bubble deformation and breakup around critical $Re$ number conditions in our study.  }
\section{Numerical Analysis}
%  \includegraphics[width=\textwidth]{1-SchematicAndGrid}
  \includegraphics[scale=0.4]{Figure/1-SchematicAndGrid}
  \caption{(a) Computational domain schematic for a bubble or drop in shear 
           flow.  Gravity is set to zero in our computations in order to isolate
           the effects of density and viscosity ratios.  
           (b) (\textit{upper panel}) a two-level adaptive mesh 
           refinement (AMR) grid schematic corresponding to one of our
           simulations;
           (\textit{lower panel}) snapshot of bubble deformation 
           in simple linear shear flow.}
  \label{fig:SchemAndGrid}

\subsection{Numerical method and governing equations}
